% !TEX program = lualatex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvtheme[black]{classic}

\usepackage{fontspec}

\usepackage[scale=0.75, margin=1.5cm]{geometry}

\usepackage{academicons}

\usepackage[style=apa,backend=biber]{biblatex}

\addbibresource{francesco_bailo_cv.bib}

\renewcommand*{\sectionfont}{\Large\mdseries\upshape}
\renewcommand*{\subsectionfont}{\large\mdseries\upshape}
\newcommand*{\subsubsectionfont}{\large\mdseries\itshape}% New subsubsection font
\newcommand*{\subsubsectionstyle}[1]{{\subsubsectionfont\textcolor{color1}{#1}}}
\makeatletter
\NewDocumentCommand{\subsubsection}{sm}{%
  \par\addvspace{1ex}%
  \phantomsection{}% reset the anchor for hyperrefs
  \addcontentsline{toc}{subsubsection}{#2}%
  \begin{tabular}{@{}p{\hintscolumnwidth}@{\hspace{\separatorcolumnwidth}}p{\maincolumnwidth}@{}}%
    \raggedleft\hintstyle{} &{\strut\subsubsectionstyle{#2}}%
  \end{tabular}%
  \par\nobreak\addvspace{0.5ex}\@afterheading}% to avoid a pagebreak after the heading
\makeatother

% Personal data
\firstname{Francesco}
\familyname{Bailo}

\address{School of Social and Political Sciences, \\ Faculty of Arts and Social Sciences, \\ University of Sydney }{}{Australia}
\phone[fixed]{+61~02~8627~6895}
% \email{Francesco.Bailo@uta.edu.au}
\email{francesco.bailo@sydney.edu.au}
\homepage{www.francescobailo.net}
% \extrainfo{\homepagesymbol\httplink{www.francescobailo.net}}

% \title{Curriculum Vitæ}
\title{CV}
\social[orcid]{0000-0001-5971-1921}
\social[googlescholar][scholar.google.com/citations?user=T_TftJUAAAAJ]{Francesco Bailo}
\social[linkedin]{frbailo}
\social[stackoverflow]{1707938}
\social[github]{fraba}

\begin{document}

\maketitle

\vspace{-1cm}


\textit{Updated: \today}

% Sydney, 2 luglio 2024

\vspace{.5cm}

I have achieved the Italian scientific qualification ("Abilitazione Scientifica Nazionale") as associate professor in the Italian higher education system in the call 2021/2023 (valid until 03/10/2033) for the disciplinary fields of \textbf{14/A2 - Political science} and \textbf{14/C2 - Sociology of culture and communication}.

\section{Academic positions}

\cventry{Jan 2023 - Present}{Lecturer in Data Analytics in the Social Sciences}{School
  of Social and Political Sciences, University of Sydney}{Sydney,
  Australia}{}{
I am responsible for conducting academic research, designing, coordinating and teaching university courses at undergraduate and postgraduate levels; supervising research students; recruiting and managing teaching and research assistants; participating in academic management and all the activities of my Faculty. \\
Since January 2023, I have been responsible for designing, coordinating and teaching the undergraduate course \textbf{Data Analytics in the Social Sciences} (with R) SSPS4102 (2023-2024) and the postgraduate courses of \textbf{Research Design} GOVT6139 (2023-204) and \textbf{Data Analytics for Social Research} (with R) SSPS6006 (2024). \\
Since 2023, I have been a member of The University of Sydney's \textbf{Human Research Ethics Committee Arts and Social Sciences Low-Risk Sub-Committee}.\\
Since 2023, I have been a \textbf{Student Advisor} for the Faculty of Arts and Social Sciences of the University of Sydney. \\
This position also entailed a component of engagement and partnership, including liaisons with internal and external stakeholders, as well as a significant research commitment. \\
More details of teaching and research activities are listed below.
}

\cventry{Mar 2019 - Jan 2023}{Lecturer in Digital and Social Media}{School
  of Communication, University of Technology Sydney}{Sydney,
  Australia}{}{
I worked as a Digital and Social Media Lecturer at the University of Technology Sydney for three years. In this role, I had teaching responsibilities, primarily as a faculty member in the \textbf{Bachelor of Communication Digital and Social Media} program. Additionally, I was involved in research and supervision of master's and doctoral students. \\
Activities carried out in this role include design, coordination, teaching, and healing supervisory responsibility for the teaching assistant team for the following courses: \textbf{Digital Media Industries} 54061 (2019 and 2020); \textbf{Code as Literacy, Commodity, Infrastructure} 54063 (2019, 2020, and 2021); \textbf{Digital Media: Marketing, Metrics, and Data} 54061 (2021); \textbf{Working with Data and Code} 52685 (2022);  \textbf{Digital Media Metrics} 52682 (2022), \textbf{Application Implementation with Microsoft Dynamics} 570002 (2022) (details of teaching activities are listed below). \\
This position also entailed a component of engagement and partnership, including liaisons with internal and external stakeholders, as well as a significant research commitment, as described in more detail below.
}

\cventry{Jan 2018 - Mar 2019}{Postdoctoral Fellow in Digital
    Media Methods}{Department of Media and Communications, the
    University of Sydney}{Sydney, Australia}{}{
In this role, I had primarily research responsibilities, which involved preparing a monograph. Additionally, I was responsible for organizing training sessions on the application of digital methods within the department and the university, benefiting colleagues and students across a range of different disciplines. \\
I was also responsible for designing, coordinating and teaching the postgraduate course of \textbf{Public opinion, policy and the public sphere} MECO6913 (2018).
}

\vspace{.5cm}

\section{Non-academic positions}

\cventry{Aug 2017 - Jan 2018}{Survey consultant}{Cambodia
    Development Resource Institute (CDRI)}{Phnom Penh, Cambodia}{}{As an external consultant for the Cambodia Development Resource Institute (CDRI) in Phnom Penh, Cambodia, I was responsible for organizing a survey of the Cambodian population regarding the use of new communication technologies and analysing the collected data.}

\cventry{Jun 2012 - Mar 2013}{Survey consultant}{Australian
    Centre for International Agricultural Research (ACIAR)}{Canberra,
    Australia}{}{As an external consultant for the Australian Centre for International Agricultural Research (ACIAR), I was responsible for conducting an impact evaluation of an Australian government development aid program in Afghanistan. This involved establishing the evaluation methodology, designing the questionnaire, negotiating with local partners, and collaborating on data analysis.}
  
\cventry{Mar 2011 - Mar 2012}{National Program
    Manager}{Mission of Assistance for the Development of
    Rural Economies in Afghanistan (MADERA)}{Kabul, Afghanistan}{}{I was responsible for managing a budget of US\$ 2.1 million and a staff of 200 people while monitoring the implementation of the National Solidarity Program in hundreds of communities distributed in four provinces of Afghanistan.}

\cventry{Feb 2009 - Feb 2010}{Specialist in Business Development}{Food and Agriculture Organization (FAO) of the United Nations}{San Marcos, Guatemala}{}{}.

\section{Education}

\cventry{Aug 2017}{Doctor of Philosophy (PhD)}{Department of
  Government and International Relations, the University of
  Sydney}{Sydney, Australia}{}{On 20 October 2023, the degree in Doctor of Philosophy was recognised in Italy by the University of Padova according to Article 38, paragraph 3.2 of Legislative Decree 165/2001.}

\cventry{Sep 2013}{Diploma in Data and Systems Analysis}{University of
  Oxford}{Oxford, United Kingdom}{}{}

\cventry{Jan 2011}{Master of Science in Public Policy and Sustainable
  Development} {Maastricht University}{Maastricht, the Netherlands}{}{}

\cventry{Apr 2008}{Master of Arts in Economics, Politics and
  International Institutions (2nd Cycle/Graduate Degree)}{University
  of Pavia}{Pavia, Italy}{}{}

\cventry{Dec 2004}{Bachelor Degree in International Studies (1st
  Cycle)}{University of Turin}{Turin, Italy}{}{}

\section{Awards and prizes}

\cvline{Nov 2023}{\emph{Teaching Award (Teaching Innovation)}. Awarded by the Faculty of Arts and Social Sciences at the University of Sydney.}

\cvline{Sep 2018}{\emph{The Internet, Policy \& Politics Conference Best
Paper Prize}. Awarded by the Oxford Internet Institute of the
University of Oxford.}

\cvline{Mar 2015}{\emph{Berlin Doctoral Fellowship}. Awarded by the
  Faculty of Arts and Social Sciences at the University of Sydney}.

\cvline{May 2013}{\emph{Full PhD Scholarship - Australian Postgraduate
    Award}. Awarded in by the University of Sydney.}

\cvline{2011}{\emph{Top 3\% Award}. Awarded by Maastricht University}.

\cvline{2005}{\emph{SEN Coimbra Group Grant}. Awarded by the
  University of Pavia}.

\cvline{2003}{\emph{Erasmus Scholarship}. Awarded by the University of
  Turin}.

\section{Teaching}

\cvlistitem{I have had formal responsibilities as a university teacher in Australia for over \textbf{nine years}.} 
\cvlistitem{My teaching experience in \textbf{digital media} and \textbf{quantitative methods} includes \textbf{statistical and data analysis}, \textbf{digital methods}, \textbf{research methods}, \textbf{data visualisation (Tableau and R)}, \textbf{network analysis}, \textbf{natural language processing}, and \textbf{coding} (\textbf{Python} and \textbf{R}) delivered to diverse audiences, including undergraduate, postgraduate and research students in the Faculty of Arts and Social Sciences but also academics and professionals.}
\cvlistitem{I have experience \textbf{coordinating large courses} (up to 300 students) and recruiting, training and supervising teaching assistants. My coordinating responsibilities have included \textbf{managing teaching staff}, \textbf{marking}, \textbf{recruiting students}, \textbf{providing pastoral care for students}, and defending academic integrity against plagiarism and cheating.}

\subsection{Undergraduate course coordinator}

\cvline{2023 - 2024}{\textbf{Data Analytics in the Social Sciences} (with R) SSPS4102. School of Social and Political Sciences, The University
  of Sydney. https://www.sydney.edu.au/units/SSPS4102}

\cvline{2021 - 2022}{\textbf{Working with Data and Code} 52685. School of Communication, University of Technology
Sydney. https://handbook.uts.edu.au/subjects/52685}

\cvline{2022}{\textbf{Digital Media Metrics} 52682. School of Communication, University of Technology
  Sydney. https://handbook.uts.edu.au/subjects/52682}

\cvline{2021}{\textbf{Digital Media: Marketing, Metrics and Data } 54061. School of Communication, University of Technology
  Sydney.}

\cvline{2019 - 2020}{\textbf{Digital Media Industries} 54005. School
  of Communication, University of Technology Sydney.}
   
\subsection{Postgraduate course coordinator}

\cvline{2024}{\textbf{Data Analytics for Social Research} SSPS6006. School of Social and Political Sciences, The University of Sydney. https://www.sydney.edu.au/units/SSPS6006}

\cvline{2023 - 2024}{\textbf{Research Design} GOVT6139. Discipline of Government and
  International Relations, School of Social and Political Sciences,
  The University of Sydney. https://www.sydney.edu.au/units/GOVT6139}

\cvline{2022}{\textbf{Application Implementation with Microsoft Dynamics} 570002. School of Communication, University of Technology
Sydney. https://handbook.uts.edu.au/subjects/details/570002}

\cvline{2018}{\textbf{Public opinion, policy and the public
    sphere} MECO6913. Department of Media and Communications,
  the University of Sydney. https://www.sydney.edu.au/units/MECO6913}

\subsection{Workshops}

\cvline{Jul 2022}{\textbf{(The art of) text mining and analysis}.
  Winter School Training Session - ANZCA. University of Canberra. https://fraba.github.io/2022-ANZCA-workshop-The-art-of-text-analysis/}

\cvline{Jul 2021}{\textbf{How to do social media data analysis using
    Tableau} (honours). School of Communication, University of Technology Sydney}

\cvline{Dec 2018}{\textbf{Topic Models in R}. DH Downunder 2018 summer
  school, Western Sydney University and the University of Sydney. https://digital-methods-sydney.github.io/ws-201812/}

\cvline{Jun 2018}{\textbf{Digital methods workshop: Social network
    analysis, Twitter data collection, text analysis and the R
    software}. Department of Media and Communications, the University
  of Sydney. https://digital-methods-sydney.github.io/ws-201806/}

\cvline{Nov - Dec 2016}{\textbf{Digital media methods: Applications of R software and RStudio to social research}. Department of Media and Communications, the University
  of
  Sydney. \url{https://fraba.github.io/digital_media_methods_sydney/}}

\subsection{Supervision of research students}

\cvlistitem{I successfully completed the supervision of \textbf{four research students (Honours Thesis)}, and I am currently supervising one research student.}

\cvlistitem{I was the primary supervisor of the \textbf{PhD student} Veronica ann Alwan (project titled: "Digital Rights in the MENA Region: Threats, Limitations and Impact") between 2021 and 2023 as faculty of the School of Communication at the University of Technology Sydney (while I am currently an external supervisor). In addition to supervising the project, I also supported the development and preparation of the student’s research proposal for the PhD program.} 

\cvlistitem{I supervised the international \textbf{PhD student} Fungai Machirori (project titled: “New Media and Contemporary Forms of Communications in Sub-saharan Africa: A Comparative Analysis of Kenya and Zimbabwe”) between 2019 and 2023 as faculty of the School of Communication a the University of Technology Sydney.}

\subsection{Guest lecturer}

\cvline{Sep 2023}{\textbf{Researching Digital Cultures} ARIN3620. Discipline of Media and Communications, University of Sydney}

\cvline{March 2023}{\textbf{Research Methods} MECO4114. Discipline of Media and Communications, University of Sydney}

\cvline{Sep 2022}{\textbf{Political Ideas and Change} 52673. School of Communication, University of Technology Sydney}

\cvline{Sep 2021}{\textbf{Political Ideas and Change} 52673. School of Communication, University of Technology Sydney}

\cvline{Sep 2018}{\textbf{Digital Tools for the Humanities} LNGS2628. Department of Linguistics, University of Sydney}

\cvline{May 2017}{\textbf{Political analysis} GOVT2991. Department of Government and International Relations, University of Sydney}

\cvline{Sep 2017}{\textbf{Introduction to Political Science} GOVT1104. Department of Government and International Relations, University of Sydney}

\cvline{Sep 2017}{\textbf{Digital Politics} GOVT3901. Department of Government and International Relations, University of Sydney}

\subsection{Teaching assistant roles}

%---------------------------------------------------------

\cvline{2019 - 2021}{\textbf{Understanding Digital Audiences} 54060. School of Communication, University of Technology Sydney}  
\cvline{2017}{\textbf{Political Analysis} GOVT2991. Department of Government and International Relations, University of Sydney}
\cvline{2017}{\textbf{Introduction to Political Science} GOVT1104. Department of Government and International Relations, University of Sydney}
\cvline{2014}{\textbf{Human Rights and
        Australian Politics} GOVT2111. Department of Government and International Relations, University of Sydney)}

\section{Research}

\subsection{Collaborations}

\cvlistitem{Since 2023, I am part of the \textbf{\href{https://computational-social-science.sydney.edu.au/people/}{Computational Social Science Lab}} at the University of Sydney.}

\cvlistitem{Since 2023, I am a \textbf{chief investigator} in a research project funded (\textbf{AU\$ 500,000}) by the Commonwealth of Australia (through the Department of Defence) and the NSW government.}

\cvlistitem{Between 2021 and 2022, I was a member of the \textbf{Technology, Media and Strategy Research Group} of the Faculty of Arts and Social Sciences at the University of Technology Sydney.}

\cvlistitem{Between 2021 and 2022, I was a member of the \textbf{Faculty Research Committee} of the Faculty of Arts and Social Sciences at the University of Technology Sydney.}

\cvlistitem{In 2021, I was a chief investigator in the project "The dynamics of disinformation across traditional and social media", funded (\textbf{AU\$ 20,000}) with a competitive grant by the Faculty of Engineering and Information Technology of the University of Technology Sydney.}

\cvlistitem{In 2020, I was a \textbf{chief investigator} in the research project "Mapping and countering the diffusion of hate speech across social media", funded by \textbf{Facebook (AU\$ 87,767)} with a competitive grant under the Content Policy Research Initiative.}

\cvlistitem{Between 2019 and 2020, as the \textbf{principal investigator} of the project "Studies on opinion diffusion and polarisation online, mixing an ethnographic approach with quantitative methods based on computational modelling of behaviour," funded with a competitive grant of \textbf{AU\$ 20,000} by the Faculty of Engineering and Information Technology at the University of Technology Sydney, \textbf{I selected and then led the research team}.}

\cvlistitem{In 2017, I was part of the research team of the "\textbf{Digital Rights} and Governance in Australia and Asia" project, which received funding through a competitive grant from the University of Sydney under the Sydney Research Excellence Initiative. I actively participated in the research activities of the University of Sydney's research group, and in my role, I contributed to organising an international workshop, which took place on 18 August 2017.}

\subsection{Consultations}

\cvlistitem{In 2023, I was invited to co-author and submit a response to the Australian Government Department of Industry, Science and Resources on the \textbf{Safe and Responsible AI in Australia Discussion Paper}.}

\cvlistitem{In 2021, I participated as expert to the \textbf{Consultation Roundtable for COVID Data Access Mandate} organised by Responsible Technology Australia.}

\cvlistitem{As a social researcher, I have collaborated as an external consultant with government agencies in two countries (\textbf{Australia} and \textbf{Cambodia}), bringing my expertise in survey design and quantitative analysis. For the Australian government, I designed and implemented a \textbf{nationwide} survey in \textbf{Afghanistan}. The survey was successfully administered in difficult conditions and resulted in an impact assessment exercise based on the data collected in the field. In \textbf{Cambodia}, I worked for a government agency to design a nationwide survey on the use of Internet technologies by the general population. In addition to the survey design, I was responsible for training the local staff to administer the survey and quantitatively analyse the data with statistical software.}  

\cvline{Citations:}{280 (\href{https://scholar.google.com.au/citations?user=T_TftJUAAAAJ}{Google Scholar}); 110
(\href{https://www.scopus.com/authid/detail.uri?authorId=57057661400}{Scopus});
81 (\href{https://www.webofscience.com/wos/author/record/AGN-9443-2022}{Web of Science})}
\cvline{H-index:}{8 (\href{https://scholar.google.com.au/citations?user=T_TftJUAAAAJ}{Google Scholar}); 
4 (\href{https://www.scopus.com/authid/detail.uri?authorId=57057661400}{Scopus});
4 (\href{https://www.webofscience.com/wos/author/record/AGN-9443-2022}{Web of Science})}

\subsection{Publications}

\subsubsection{Book}

\cvlistitem{\fullcite{bailo_online_2020}}

\subsubsection{Articles published in refereed journals}

\cvlistitem{\fullcite{tronconi_Other_2024}}

\cvlistitem{\fullcite{johnsLabellingShadowBans2024}}

\cvlistitem{\fullcite{bailo_riding_2023}}

\cvlistitem{\fullcite{kong_slipping_2022}}

\cvlistitem{\fullcite{bailo_no_2021}}

\cvlistitem{\fullcite{bailo_institutional_2021}}

\cvlistitem{\fullcite{abbondanza_electoral_2018}}

\cvlistitem{\fullcite{bailo_hybrid_2017}}

\cvlistitem{\fullcite{vromen_everyday_2016}}

\cvlistitem{\fullcite{bailo_mapping_2015}}

\subsubsection{Book sections}

\cvlistitem{\fullcite{sengulTwentyfirstCenturyPopulism2023}}

\cvlistitem{\fullcite{bailo_social_2023b}}

\subsubsection{Research reports}

\cvlistitem{\fullcite{flew_safe_2023}}

\cvlistitem{\fullcite{goggin_digital_2017}}

\cvlistitem{\fullcite{jilani_aciar_2013}}

\subsubsection{PhD thesis}

\cvlistitem{\fullcite{bailo_citizen_2017}}

\subsubsection{News articles}

\cvlistitem{\fullcite{johns_Conspiracy_2024}}

\cvlistitem{\fullcite{bailo_social_2023a}}

\cvlistitem{\fullcite{bailo_ignore_2022}}

\cvlistitem{\fullcite{meese_its_2021}}

\cvlistitem{\fullcite{bailo_would_2021}}

\cvlistitem{\fullcite{bailo_il_2019-1}}

\cvlistitem{\fullcite{bailo_il_2019-1}}

\subsection{External grants}

\cvline{2023}{\emph{Commonwealth of Australia (through the Department of Defence) and the NSW government}. AU\$500,000}

\cvline{Sep 2019}{\emph{Facebook Content Policy Research
    Award}. US\$60,000. Awarded by Facebook. Investigators: Dr Amelia
  Johns (University of Technology Sydney), Dr Francesco Bailo (University of Technology Sydney) and Dr Marian-Andrei Rizoiu (University of Technology Sydney).}

\subsection{Internal grants}

\cvline{May 2021}{\emph{Cross-Faculty Collaboration
    Scheme}. AU\$20,000. Awarded by the University of Technology Sydney. Chief Investigators: Dr Marian-Andrei Rizoiu (University of Technology Sydney), Dr Amelia Johns (University of Technology Sydney), Dr Francesco Bailo (University of Technology Sydney), Dr Anne Kruger (First Draft, University of Technology Sydney), Prof Derek Wilding and Monica Attard (Centre for Media Transition, University of Technology Sydney).}

\cvline{Aug 2019}{\emph{Early Career Research Grant}. AU\$15,000. Awarded by the Faculty of Arts and Social Sciences (University of Technology Sydney). }

\cvline{Sep 2019}{\emph{Cross-faculty Collaboration Scheme}. AU\$20,000. Awarded by the Faculty of Engineering and Information Technology (University of Technology Sydney). Chief Investigators: Dr Francesco Bailo (University of Technology Sydney), Dr Amelia Johns (UTS) and Dr Marian-Andrei Rizoiu (University of Technology Sydney).}

\cvline{May 2018}{\emph{Research Support Scheme}. AU\$2,500. Awarded by the School of Literature, Art and Media (the University of Sydney).}	

\section{Media appearances}

\cvlistitem{\fullcite{obrienABCNewsHour2024}}

\cvlistitem{\fullcite{evershed_News_2024}}

\cvlistitem{\fullcite{gugoleRelazioniTraItalia2024}}

\cvlistitem{\fullcite{corsetti_could_2022}}

\cvlistitem{\fullcite{bogle_one_2022}}

\cvlistitem{\fullcite{nagata_tiktokers_2022}}

\cvlistitem{\fullcite{lin_tiktoks_2022}}

\cvlistitem{\fullcite{contreras_i_2021}}

\cvlistitem{\fullcite{oneil_who_2021}}

\cvlistitem{\fullcite{purtill_facebook_2021}}

\cvlistitem{\fullcite{walden_disgusted_2021}}

\cvlistitem{\fullcite{knaus_how_2021}}

\cvlistitem{\fullcite{megalokonomos_what_2020}}

\cvlistitem{\fullcite{gillespie_pastel_2020}}

\cvlistitem{\fullcite{moffitt_populism_2018}}

\section{Presentations}

\cventry 
{23 June 2024}
{Presenter with Francesco Marolla, Marilù Miotto and Giovanni Cassani (paper)}
{74th Annual ICA Conference}
{Gold Coast, Australia}
{}
      {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Affording fragmented audiences: Multi-platform deliberation within the Five Star Movement'.}
      \end{itemize}
    }

\cventry 
{7 December 2023}
{Presenter with Giulia Sandri and Anontella Seddone (paper)}
{2023 Australian Society for Quantitative Political Science Conference}
{Brisbane, Australia}
{}
      {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Levelling at the margin: Personal networks, social capital and the Internet in the mobilisation of the Five Star Movement'.}
      \end{itemize}
    }


\cventry 
{27 November 2023}
{Presenter (paper)}
{Australian Social Network Analysis Conference (ASNAC) 2023}
{Sydney, Australia}
{}
      {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Measuring information disorder'.}
      \end{itemize}
    }

\cventry 
{6 September 2023}
{Presenter with Giulia Sandri and Anontella Seddone (paper)}
{ECPR General Conference}
{Prague, Czech Republic}
{}
      {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Online and offline social capital as catalyst for political mobilisation: the case of digital native political parties'.}
      \end{itemize}
    }

\cventry 
{1 June 2023}
{Presenter}
{Big Data and Textual Analysis in Economics, Finance, and Politics Workshop}
{Sydney, Australia}
{}
      {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Ideology and the collective construction of knowledge of unfolding events on Wikipedia'.}
      \end{itemize}
    }

\cventry 
{11 May 2023}
{Presenter}
{Wiki Workshop 2023}
{Virtual}
{}
      {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Ideology and the collective construction of knowledge of unfolding events on Wikipedia'.}
      \end{itemize}
    }
 
\cventry % Melbourne disinformation
{19 July 2022}
{Presenter with Amelia Johns}
{ADM+S (Automated Decision-Making and Society) Misinformation Workshop}
{Melbourne, Australia}
{}
      {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Controlling authentically spread misinformation: Practical and Ethical
Challenges for platform moderation, Mapping and Countering the Diffusion of Hate Speech Across Social Media'.}
      \end{itemize}
    }

\cventry % Sunbelt # https://www.sunbelt2022.org/
{14 July 2022}
{Presenter with Amelia Johns and Marian-Andrei Rizoiu (paper)}
{International Network for Social Network Analysis (INSNA) Sunbelt 2022 Conference}
{Cairns, Australia}
{}
       {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Riding Information Crises: The
            Australian Far-right community in the Twittersphere'.}
      \end{itemize}
    }

\cventry % https://sicss.io/2022/sydney/schedule
{28 June 2022}
{Panelist}
{Academy of the Social Sciences in Australia Workshop}
{Sydney, Australia}
{}
       {
      \begin{itemize} % Description(s)
        \item {Panel title: `Teaching computational social science'.}
      \end{itemize}
    }

\cventry % ICWSM 2022
% https://www.icwsm.org/2022/index.html/
{6-9 June 2022}
{Author with Quyu Kong, Emily Booth, Amelia Johns, Marian-Andrei Rizoiu (paper)}
{16th International Conference on Web and Social Media}
{Atlanta, Georgia}
{}
       {
      \begin{itemize} % Description(s)
        \item {Paper title:`Slipping to the {Extreme}: {A} {Mixed} {Method} to {Explain} {How} {Extreme} {Opinions} {Infiltrate} {Online} {Discussions}'.}
      \end{itemize}
    }
    
\cventry % AOIR2021 https://spir.aoir.org/ojs/index.php/spir/article/view/12091/10227
{13-16 Oct 2021}
{Presenter with James Meese and Edward Hurcombe (paper)}
{The 22nd Annual Conference of the Association of Internet Researchers
  (AOIR)}
{Melbourne, Australia}
{}
       {
      \begin{itemize} % Description(s)
        \item {Presentation title:`The institutional impacts of algorithmic distribution: Facebook and the Australian news media'.}
      \end{itemize}
    }

\cventry % https://auspsa.org.au/2021-apsa-conference/
{20-22 September 2021}
{Presenter with Kurt Sengul (paper)}
{2021 Australian Political Studies Association (APSA) Conference: Politics in the Age of Uncertainty}
{Virtual conference}
{}
       {
      \begin{itemize} % Description(s)
        \item {Presentation title:`21st century populism in Australia and in Italy: A comparative analysis'.}
      \end{itemize}
    }

 \cventry
    {8-11 September 2021}
    {Presenter with Gabriele Abbondanza (paper)}
    {Società Italiana di Scienza Politica (SISP) Conference 2021}
    {Virtual conference}{}
       {
      \begin{itemize} % Description(s)
        \item {Presentation title:`COVID-19 and human security: environmental, social, and medical risk factors'.}
      \end{itemize}
    }


\cventry % ANZCA http://anzca.org/conference/2021
{9 July 2021}
{Presenter with Amelia Johns (paper)}
{Australian and New Zealand Communication Association (ANZCA) Conference}
{Melbourne, Australia}
{}
       {
      \begin{itemize} % Description(s)
        \item {Presentation title:`Have Facebook's policy changes
            addressed the circulation of health misinformation on its
            platform during COVID-19? Findings from a study monitoring
            anti-vax and far-right public pages (2019-2021)'.}
      \end{itemize}
    }

\cventry % ANZCA
{9 July 2021}
{Presenter with James Meese and Edward Hurcombe (paper)}
{Australian and New Zealand Communication Association (ANZCA) Conference}
{Melbourne, Australia}
{}
       {
      \begin{itemize} % Description(s)
        \item {Presentation title:`The institutional impacts of algorithmic distribution: Facebook and the Australian news media'.}
      \end{itemize}
    }


\cventry
{17-18 September 2020}
{Presenter with Amelia Johns and Marian-Andrei Rizoiu}
{Facebook's 2019 Content Policy Research Initiative Conference}
{Virtual conference}
{}
       {
      \begin{itemize} % Description(s)
        \item {Presentation title:`Mapping and countering the diffusion of hate speech across social media'.}
      \end{itemize}
    }


\cventry
    {1-2 July 2019} % Date(s)
    {Presenter (paper)} % Role
    {Social Movements and Parties in a Fractured Media Landscape} % Event
    {Florence, Italy} % Location
        {}
        {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Bridging the Void. Distress, Participation and the
Electoral Success of the Five Star Movement (2005-2018)'.}
      \end{itemize}
    }


 %---------------------------------------------------------
    \cventry
        {1-2 July 2019} 
    {Presenter (paper)} % Role
    {Social Movements and Parties in a Fractured Media Landscape} % Event
    {Florence, Italy} % Location
% Date(s)
        {}
    {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Bridging the Void. Distress, Participation and the
Electoral Success of the Five Star Movement (2005-2018)'.}
      \end{itemize}
    }
 
%---------------------------------------------------------
    \cventry
       {23 November 2018} % Date(s)
    {Presenter (paper)} % Role
    {Data and politics seminar (United States Studies Centre)} % Event
    {Sydney, Australia} % Location
 {}
    {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Social capital, Internet capital and the recruitment networks of political movements: A theoretical and empirical approach'.}
      \end{itemize}
    }

  
%---------------------------------------------------------
    \cventry
      {3 October 2018} % Date(s)
    {Invited speaker} % Role
    {Gale Digital Scholar Lab Roadshow} % Event
    {Sydney, Australia} % Location
  {}
    {
      \begin{itemize} % Description(s)
        \item {Presentation title: `Racism in online interactions: Comparing survey data and social media data'.}
      \end{itemize}
    }

%---------------------------------------------------------
    \cventry
        {25-28 September 2018} % Date(s)
    {Presenter (paper)} % Role
    {\href{http://dha-2018.p.dha2018.currinda.com/days/2018-09-28}{Digital Humanities Australasia 2018}} % Event
    {Adelaide, Australia} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: `Local participation and the Five Star Movement’s results in the 2018 General Election'.}
      \end{itemize}
    }


%---------------------------------------------------------
    \cventry
        {20-21 September 2018} % Date(s)
    {Presenter (paper)} % Role
    {\href{http://blogs.oii.ox.ac.uk/policy/ipp-conference/papers/}{The Internet, Policy \& Politics academic conference}} % Event
    {Oxford, UK} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {\href{http://blogs.oii.ox.ac.uk/policy/wp-content/uploads/sites/77/2018/09/IPP2018-Bailo.pdf}{Paper title: `Internet-mediated recruitment networks of political movements: Empirical and theoretical approach'}.}
      \end{itemize}
    }


%---------------------------------------------------------
    \cventry
        {18 July 2018} % Date(s)
    {Presenter (paper)} % Role
    {\href{https://www.canberra.edu.au/research/faculty-research-centres/nmrc/news-and-events/events/digital-participation}{Information for Digital Participation Symposium}} % Event
    {Canberra, Australia} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: `Local participation and the Five Star Movement’s results in the 2018 General Election'.}
      \end{itemize}
    }


%---------------------------------------------------------
    \cventry
      {16-17 November 2016} % Date(s)
    {Presenter (poster)} % Role
    {1st Australian Social Network Analysis Conference} % Event
    {Hawthorn, Australia} % Location
  {}
    {
      \begin{itemize} % Description(s)
        \item {Poster title: `Political stability and the fragmentation of online publics in multilingual states'.}
      \end{itemize}
    }

%---------------------------------------------------------
    \cventry
        {22-23 September 2016} % Date(s)
    {Presenter (paper)} % Role
    {\href{http://ipp.oii.ox.ac.uk/2016}{Internet, Politics, and Policy Academic Conference}} % Event
    {Oxford, UK} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: \href{http://ipp.oii.ox.ac.uk/2016/programme-2016/track-a-politics/participation-ii-networks-and/francesco-bailo-political-stability-and}{`Political stability and the fragmentation of online publics in multilingual states'}.}
      \end{itemize}
    }

%---------------------------------------------------------

    \cventry
        {15-18 June 2016} % Date(s)
    {Presenter (paper)} % Role
    {The 8th Pan-European Conference on the European Union} % Event
    {Trento, Italy} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title:  \href{http://ecpr.eu/Events/PaperDetails.aspx?PaperID=27234&amp;EventID=105}{`From Five Stars to ground: A quantitative content analysis of Beppe Grillo's blogposts'}.}
      \end{itemize}
    }

    \cventry
        {28-30 September 2015} % Date(s)
    {Presenter (papers)} % Role
    {\href{http://www.auspsa.org.au/page/apsa-conference-2015-0}{Australian Political Studies Association Annual Conference}} % Event
    {Canberra, Australia} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: `Networks in the online mobilisation enterprise of Italy's Five Star Movement'.}
        \item {Paper title: `Between anti-elite populism and policy: A textual analysis of the relation between Beppe Grillo's posts and his commenters'.}
      \end{itemize}
    }

    \cventry
        {11-8 June 2015} % Date(s)
    {Presenter (poster)} % Role
    {\href{http://www.iccss2015.eu/}{International Conference on Computational Social Science}} % Event
    {Helsinki, Finland} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Poster title:  \href{http://www.francescobailo.net/wordpress/wp-content/uploads/2016/04/f_bailo_poster_iccss15_original.pdf}{`Networks in the online mobilisation enterprise of Italy's Five Star Movement'}.}
      \end{itemize}
    }

    \cventry
        {12-13 February 2015} % Date(s)
    {Presenter (paper)} % Role
    {\href{https://devpolicy.crawford.anu.edu.au/annual-australasian-aid-conference/2015}{Australasian Aid Conference}} % Event
    {Canberra, Australia} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title:  \href{http://devpolicy.org/2015-Australasian-aid-conference/presentations/2b/Guglielmo-Briscese-and-Francesco-Bailo.pdf}{'Official development assistance vs People2People microlending: the case of Australia'} (with Guglielmo Briscese).} 
      \end{itemize}
    }

    \cventry
        {5-6 December 2014} % Date(s)
    {Presenter (paper)} % Role
    {\href{http://www.asqps.org.au/index.php/asqps/2014"}{Third Annual Conference of the Australian Society for Quantitative Political Science}} % Event
    {Sydney, Australia} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: `Heterogeneity and fragmentation in online political discussion: A comparative and within-case study analysis of the forums of Italy's Five Star Movement and Germany's Pirate Party'.}
      \end{itemize}
    }

    \cventry
    {9-10 October 2014} % Date(s)
    {Presenter (papers)} % Role
    {New forms of Digital Communication and Political Organisation} % Event
    {Canberra, Australia} % Location
    {}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: `Heterogeneity and fragmentation in online political discussion : A comparative and within-case study analysis of the forums of Italy's Five Star Movement and Germany’s Pirate Party'.}
         \item{Paper title: `From \#MarchinMarch to \#BustTheBudget: Comparing social media ecologies of Australian protest events' (with Professor Ariadne Vromen).}
      \end{itemize}
    }

    \cventry
        {28 September-1 October 2014} % Date(s)
    {Presenter (paper)} % Role
    {\href{https://sites.google.com/site/apsa2014/home}{Australian Political Studies Association Annual Conference}} % Event
    {Sydney, Australia} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: `Prestige in online political talks: A case study of users' behaviour within the media system of the Five Star Movement'.}
      \end{itemize}
    }

    \cventry
        {25-26 September 2014} % Date(s)
    {Presenter (paper)} % Role
    {\href{http://ipp.oii.ox.ac.uk/2014}{Internet, Politics, and Policy Academic Conference}} % Event
    {Oxford, UK} % Location
{}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: \href{http://ipp.oii.ox.ac.uk/2014/programme-2014/track-d-networked-politics/political-and-personal-networks/francesco-bailo-mapping-online-political}{`Mapping online political talks through network analysis: A case study of the website of Italy's Five Star Movement'}.}
      \end{itemize}
    }

    \cventry
     {2-3 December 2013} % Date(s)
    {Presenter (paper)} % Role
    {Citizen Engagement and New Forms of Political Participation Workshop} % Event
    {Canberra, Australia} % Location
    {}
    {
      \begin{itemize} % Description(s)
        \item {Paper title: `Mapping online political forums through network analysis: A case study of the website of Italy's Five Star Movement'.}
      \end{itemize}
    }

\section{Skills}

  \cvline
    {Programming languages} % Category
    {\textsc{R}, Python, LaTeX, \textsc{Php},  Stata.} 

  \cvline
    {Teaching applications} % Category
    {Canvas, Blackboard, Student Relationship Engagement System (SRES), Menti, Padlet.} 

  \cvline
    {Software} % Category
    {RStudio, Tableau, \textsc{Qgis}, Linux, OpenStack (for cloud computing), \textsc{Spss}, OpenRefine, protégé.} 

  \cvline
    {Database} % Category
    {SQLite, MySQL, PostgreSQL, PostGIS, \textsc{Sparql}.} % Skills

  \cvline
    {Web} % Category
    {Wikibase, WordPress, D3.js, R Shiny.} % Skills

  \cvline
    {Languages} % Category
    {English (fluent), Spanish (working knowledge), French (basic knowledge), Italian (native).} % Skills

\end{document}
% Local Variables:
% TeX-engine: luatex
% End:      